\chapter*{Related publications}

If making use of MCStylistic code in a publication, please include a citation such as `we made use of MCStylistic-Jun2014 \citep*{collins2011b}, available from \href{http://www.tomcollinsresearch.net}{http://www.tomcollinsresearch.net}.'

For more specific use of code in Secs.~\ref{sec:stravinsqi}, \ref{sec:func-harm-anal}, or \ref{sec:query-staff-notation}, please cite the following conference paper.

\begin{quotation}
\noindent Tom Collins. Stravinsqi/De Montfort University at the MediaEval 2014 C@merata task. In \emph{Proceedings of the MediaEval 2014 Workshop}, 6 pages, Barcelona, 2014.
\end{quotation}

\noindent For Secs.~\ref{sec:ex:Racchman-Oct2010}, \ref{sec:ex:Racchmaninof-Oct2010}, or \ref{sec:markov-models}, please cite the following journal paper.

\begin{quotation}
\noindent Tom Collins, Robin Laney, Alistair Willis, and Paul H.~Garthwaite. Developing and evaluating computational models of musical style. \emph{Artificial Intelligence for Engineering Design, Analysis and Manufacturing}, in press.
\end{quotation}

\noindent For Secs.~\ref{sec:disc&rate-musical-patterns} or \ref{sec:pattern-rating}, please cite the following journal paper.

\begin{quotation}
\noindent Tom Collins, Robin Laney, Alistair Willis, and Paul H.~Garthwaite. Modelling pattern importance in Chopin's mazurkas. \emph{Music Perception}, 28(4):387-414, 2011.
\end{quotation}

% \vspace{0.5cm}
\noindent For code in Secs.~\ref{sec:disc&rate-musical-patterns} or \ref{sec:pattern-discovery}, please cite the following conference paper.

\begin{quotation}
\noindent Tom Collins, Jeremy Thurlow, Robin Laney, Alistair Willis, and Paul H.~Garthwaite. A comparative evaluation of algorithms for discovering translational patterns in Baroque keyboard works. In J.~Stephen Downie and Remco Veltkamp, editors, \emph{Proceedings of the International Symposium on Music Information Retrieval}, pages 3-8, Utrecht, 2010. International Society for Music Information Retrieval.
\end{quotation}

% \vspace{0.5cm}
\noindent If making use of any other code, please cite my thesis.

\begin{quotation}
\noindent Tom Collins. \emph{Improved methods for pattern discovery in music, with applications in automated stylistic composition}. PhD thesis, Faculty of Mathematics, Computing and Technology, The Open University, 2011.
\end{quotation}

